Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-10-31 R0V0.tex
small changes. Add todo

@@

\begin{definition}\label{def:}
	a
\end{definition}

>>>>

\todo[inline]{Scalable diagonal dominance}

@@

\begin{definition}
	A matrix $M\in\mathbb{R}^{n\times n}$ is said to be \emph{diagonally dominant} if, for every index $i\in\mathbb{N}_{[1,n]}$, the inequality $2|a_{ii}|\geq\sum_{i=1}^n |a_{ij}|$ holds. It is said to be \emph{scalable diagonally dominant} if there exists a diagonal matrix $D$ such that $DAD$ is diagonally dominant.
\end{definition}
